General constraints on magic distillation protocols from statistical mechanics

### 2021-04-26 magic_paper.tex
Typo corrected. Missing \beta terms
added numerical bounds and discussion

The mana bound can be directly calculated as
\begin{equation}
	R \leq \frac{\mana{\rho_{\rm{S}}(\epsilon)}}{\mana{\rho_{\rm{S}}(0)}} = 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}}.
\end{equation}
For the noisy Strange state, the max--thauma bound coincides with the mana bound, and are both looser than the majorization bound we derived via the first elbow constraint as illustrated in~\cref{fig:distill_bounds}. 
\begin{figure}[t]
    \centering
    \includegraphics[scale=0.45]{figs/distill_bounds.pdf}
    \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by the first elbow majorisation constraint, mana and max--thauma are plotted for $\epsilon' = 0$, up to noise level $\epsilon = 3/7$.
    Majorisation provides stricter rates than the global mana and max--thauma bounds.
    }
    \label{fig:distill_bounds}
\end{figure}

I include in~\cref{fig:test} the mana and max--thauma bounds for the purification of (a) Norrell states and (b) $T$ states.
\nick{Delete this probably?}

\begin{figure}[h]
    \centering
    \subfigure[][]{%
    \label{fig:norrell}%
    \includegraphics[height=3cm]{figs/compare_norrell.pdf}
    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:tstate}%
    \includegraphics[height=3cm]{figs/compare_tstate.pdf}}
    \caption{\textbf{Bound comparison} 
    \subref{fig:norrell} Norrell state purification; \subref{fig:tstate} $T$ state purification; \nick{Delete this probably?}
    }%
    \label{fig:test}
\end{figure}

@@

So given the ability to assume that the smallest entry of $\t$ is the $t_0$ component this means that for noise levels below $3/7$ the largest component of $\tilde{w}_{n,i_0, i_1, \dots, i_8}$ occurs at $(i_0,i_1, \dots, i_8) = (n,0,0,\dots ,0)$. We therefore have, for the no-multiplicity case, that the first elbow occurs at the point $(t_0^n, v^n)$. This will lead to a bound expression in terms of $\epsilon$ for the output state, together with whatever value $t_0$ takes on. \ddd{[give expression]}. While this is fine, we need to link $t_0$ to the physics of the state $\tau = e^{-\beta H}/\Z$. Well, just from the definition we have that
\begin{equation}
t_0 = \frac{1}{d\Z}\tr [ A_{0,0} e^{-\beta H}],
\end{equation}
where, of course, $d=3$. So in $t_0^n$ we immediately get a term $\Z^{-n} = e^{-nF}$, which is nice and general. Using the expansion of the thermal state into its energy eigenstates we obtain
\begin{align}
t_0^n &= \left ( \frac{1}{d\Z}\tr [ A_{0,0} e^{-\beta H}] \right )^n \nonumber \\
&= \frac{e^{-nF}}{3^n} ( \tr [ A_{0,0} \sum_k e^{-\beta E_k} |\varphi_k\>\<\varphi_k|])^n\nonumber \\
&= \frac{e^{-nF}}{3^n} ( \sum_k \alpha_k e^{-\beta E_k})^n,
\end{align}
where we define
\begin{equation}
\alpha_k := \<\varphi_k |A_{0,0} |\varphi_k\>, \mbox{ for }k=0,1,2.
\end{equation}
However $A_{0,0} = \sum_{r\in \mathbb{Z}_3} | -r\>\<r|$ and so
\begin{equation}
\alpha_k := \sum_{r \in \mathbb{Z}_3} \<\varphi_k |-r\> \<r |\varphi_k\>.
\end{equation}
This just encodes how the energy eigenbasis of the Hamiltonian $H$ relates to the \emph{stabilizer} basis. Anyhow, the nice thing is that we always get the Free energy term emerging in the $t_0^n$ and so we can include this into the distillation bound, with the $\alpha_k$ terms simply handling the messy issue of how the two important bases relate. We can package the messy details into some definition in some way. E.g. the form of the sum involving $\alpha_k$ looks a bit like a partition function, so we can define something like
\begin{equation}
\zeta :=  \sum_k \alpha_k e^{-\beta E_k},
\end{equation}
so that
\begin{equation}
t_0^n = \frac{e^{-nF}}{3^n}\zeta^n,
\end{equation}
which is tidy....and we could also then define $\phi$ as a kind of free energy term via $\zeta =: e^{-\beta \phi}$. This then simplifies things to
\begin{equation}
t_0^n =  \frac{e^{-n(F+\phi)}}{3^n},
\end{equation}
where $F$ corresponds to the physical free energy of $\tau$ while $\phi$ is some weird term that captures the degree to which the energy basis differs from the stabilizer basis. \ddd{[Details need tidying/checking and we need the final bounds to be computed.]}

>>>>

The mana bound can be directly calculated as
\begin{equation}
	R \leq \frac{\mana{\rho_{\rm{S}}(\epsilon)}}{\mana{\rho_{\rm{S}}(0)}} = 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}}.
\end{equation}
For the noisy Strange state, the max--thauma bound coincides with the mana bound, and are both looser than the majorization bound we derived via the first elbow constraint as illustrated in~\cref{fig:distill_bounds}. 
Numerical, ``optimal'', bounds $R_{\rm{opt}}$ obtained by considering the entirety of the Lorenz curves have been included in the plot as well, highlighting that the first elbow constraint does not capture the full capabilities of majorization.
Notably, and in contrast with the first elbow, mana and max--thauma bounds, $R_{\rm{opt}}$ depends on the copies $m,n$, in the sense that it doesn't bound their ratio $m/n$, but it is specific to the process.
\begin{figure}[t]
    \centering
    \includegraphics[scale=0.45]{figs/distill_bounds.pdf}
    \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by the first elbow majorisation constraint, mana and max--thauma are plotted for $\epsilon' = 0$, up to noise level $\epsilon = 3/7$.
    Majorisation provides stricter rates than the global mana and max--thauma bounds.
    Numerical bounds $R_{\rm{opt}}$ obtained by full Lorenz curve comparison for some processes with even number of copies up to 30 are also plotted illustrating that the first elbow constraint can be improved.
    }
    \label{fig:distill_bounds}
\end{figure}

@@

So given the ability to assume that the smallest entry of $\t$ is the $t_0$ component this means that for noise levels below $3/7$ the largest component of $\tilde{w}_{n,i_0, i_1, \dots, i_8}$ occurs at $(i_0,i_1, \dots, i_8) = (n,0,0,\dots ,0)$. We therefore have, for the no-multiplicity case, that the first elbow occurs at the point $(t_0^n, v^n)$. This will lead to a bound expression in terms of $\epsilon$ for the output state, together with whatever value $t_0$ takes on. \ddd{[give expression]}. While this is fine, we need to link $t_0$ to the physics of the state $\tau = e^{-\beta H}/\Z$. Well, just from the definition we have that
\begin{equation}
t_0 = \frac{1}{d\Z}\tr [ A_{0,0} e^{-\beta H}],
\end{equation}
where, of course, $d=3$. So in $t_0^n$ we immediately get a term $\Z^{-n} = e^{-n\beta F}$, which is nice and general. Using the expansion of the thermal state into its energy eigenstates we obtain
\begin{align}
t_0^n &= \left ( \frac{1}{d\Z}\tr [ A_{0,0} e^{-\beta H}] \right )^n \nonumber \\
&= \frac{e^{-n\beta F}}{3^n} ( \tr [ A_{0,0} \sum_k e^{-\beta E_k} |\varphi_k\>\<\varphi_k|])^n\nonumber \\
&= \frac{e^{-n \beta F}}{3^n} ( \sum_k \alpha_k e^{-\beta E_k})^n,
\end{align}
where we define
\begin{equation}
\alpha_k := \<\varphi_k |A_{0,0} |\varphi_k\>, \mbox{ for }k=0,1,2.
\end{equation}
However $A_{0,0} = \sum_{r\in \mathbb{Z}_3} | -r\>\<r|$ and so
\begin{equation}
\alpha_k := \sum_{r \in \mathbb{Z}_3} \<\varphi_k |-r\> \<r |\varphi_k\>.
\end{equation}
This just encodes how the energy eigenbasis of the Hamiltonian $H$ relates to the \emph{stabilizer} basis. Anyhow, the nice thing is that we always get the Free energy term emerging in the $t_0^n$ and so we can include this into the distillation bound, with the $\alpha_k$ terms simply handling the messy issue of how the two important bases relate. We can package the messy details into some definition in some way. E.g. the form of the sum involving $\alpha_k$ looks a bit like a partition function, so we can define something like
\begin{equation}
\zeta :=  \sum_k \alpha_k e^{-\beta E_k},
\end{equation}
so that
\begin{equation}
t_0^n = \frac{e^{-n\beta F}}{3^n}\zeta^n,
\end{equation}
which is tidy....and we could also then define $\phi$ as a kind of free energy term via $\zeta =: e^{-\beta \phi}$. This then simplifies things to
\begin{equation}
t_0^n =  \frac{e^{-n \beta (F+\phi)}}{3^n},
\end{equation}
where $F$ corresponds to the physical free energy of $\tau$ while $\phi$ is some weird term that captures the degree to which the energy basis differs from the stabilizer basis. \ddd{[Details need tidying/checking and we need the final bounds to be computed.]}
